\documentclass[letterpaper,11pt]{article}

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{paracol}

% Define colors
\definecolor{primaryblue}{RGB}{41, 98, 255}
\definecolor{darkgray}{RGB}{50,50,50}
\definecolor{mediumgray}{RGB}{80,80,80}
\definecolor{lightgray}{RGB}{240,240,240}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\parindent}{0pt}

% Section formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries\color{mediumgray}
}{}{0em}{}[\color{mediumgray}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{#1 \vspace{-1pt}}
}

\newcommand{\resumeSubheading}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\normalsize#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item[]
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \normalsize\textbf{#1} & \small\textit{#2}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=12pt, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\bfseries\color{darkgray} ISURU SAJAN} \\[3pt]
    {\Large\color{mediumgray} Full-Stack Developer} \\[6pt]
    \normalsize
    \faPhone\ +94 075 4796 701 $|$
    \href{mailto:isurusajan9@gmail.com}{\textcolor{primaryblue}{\faEnvelope\ isurusajan9@gmail.com}} \\
    \href{https://linkedin.com/in/isuru-sajan}{\textcolor{primaryblue}{\faLinkedin\ linkedin.com/in/isuru-sajan}} $|$
    \href{https://github.com/isurusajan}{\textcolor{primaryblue}{\faGithub\ github.com/isurusajan}} $|$
    \href{https://myportofolioisuru.netlify.app/}{\textcolor{primaryblue}{\faGlobe\ Portfolio}} $|$
    \faMapMarker\ Galle, Sri Lanka
\end{center}
\vspace{-8pt}

% Two column layout
\setlength{\columnsep}{0.35in}
\begin{paracol}{2}

% LEFT COLUMN
\section{Technical Skills}
\textbf{\normalsize Languages} \\
\normalsize Java, JavaScript, Python, SQL, CSS3, HTML

\vspace{5pt}
\textbf{\normalsize Frontend} \\
\normalsize React.js, Responsive Design

\vspace{5pt}
\textbf{\normalsize Backend} \\
\normalsize Node.js, Express.js, PHP, Spring Boot

\vspace{5pt}
\textbf{\normalsize Databases} \\
\normalsize MongoDB, MySQL

\vspace{5pt}
\textbf{\normalsize Tools \& Cloud} \\
\normalsize Git, GitHub, VS Code, Postman, AWS, Netlify, Vercel

\vspace{5pt}
\textbf{\normalsize Communication} \\
\normalsize English (Fluent), Sinhala (Native)

\section{Education}
\textbf{\normalsize Institute of Technology,} \\
\textbf{\normalsize University of Moratuwa} \\
\normalsize Higher National Diploma in IT \\
\normalsize GPA: 2.93 (Pursuing)

\vspace{7pt}
\textbf{\normalsize Mahinda College, Galle} \\
\normalsize G.C.E. A/L Physical Science \\
\normalsize Combined Maths (B), Physics (C), \\
Chemistry (B)

\section{Certifications}
\normalsize
\begin{itemize}[leftmargin=12pt, itemsep=1pt]
    \item AWS Essential Training(Linkedin learning)
    \item Learning GitHub(linkedin learning)
    \item WordPress Development(Cousera)
    \item JavaScript Language(Linkedin learning)
    \item Web Design Fundamentals(DP Education)
\end{itemize}

\section{References}
\textbf{\normalsize Mrs. Uthpala Athukorala} \\
\small Head of Division of IT \\
ITU Moratuwa \\
\faPhone\ +94 772 666 602 \\
\href{mailto:uthpala@itum.mrt.ac.lk}{\faEnvelope\ uthpala@itum.mrt.ac.lk}

\vspace{7pt}
\textbf{\normalsize Ms. Tharukshi Adasuriya} \\
\small Lecturer of Division of IT \\
ITU Moratuwa \\
\faPhone\ +94 771 902 981 \\
\href{mailto:tharukshin@itum.mrt.ac.lk}{\faEnvelope\ tharukshin@itum.mrt.ac.lk}

\switchcolumn

% RIGHT COLUMN
\section{Professional Summary}
\normalsize
Ambitious IT undergraduate with hands-on experience in full-stack development using the MERN stack. Proven ability to build scalable web applications with modern frameworks and RESTful APIs. Quick learner passionate about creating impactful technology solutions.

\section{Key Projects}
\vspace{-1pt}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Smart Restaurant Management System}}{}
        \vspace{-3pt}
        \textit{\small (MERN Stack, Socket.io,Nodemailer, JWT, AWS)} \\
        \vspace{-2pt}
        \resumeItemListStart
            \resumeItem{Built comprehensive restaurant platform with real-time order tracking, QR code ordering, table reservations, and analytics dashboard.}
            \resumeItem{manage and monitor restaurant operations from any device, deployed on AWS with scalable architecture.}
            \resumeItem{\href{https://github.com/Isurusajan/Mian_Taste}{\textcolor{primaryblue}{github.com/Isurusajan/Mian\_Taste}}}
        \resumeItemListEnd
        
    \resumeProjectHeading
        {\textbf{Theater Seat Booking System}}{}
        \vspace{-3pt}
        \textit{\small (React.js, Spring Boot, MongoDB, JWT)} \\
        \vspace{-2pt}
        \resumeItemListStart
            \resumeItem{Developed full-stack booking platform with movie browsing, dynamic seat reservation, and admin dashboard.}
            \resumeItem{Implemented secure user authentication and real-time seat availability updates.}
            \resumeItem{\href{https://github.com/isurusajan/theater-booking-system}{\textcolor{primaryblue}{github.com/isurusajan/theater-booking-system}}}
        \resumeItemListEnd
        
    \resumeProjectHeading
        {\textbf{AI Study Buddy}}{}
        \vspace{-3pt}
        \textit{\small (React.js, Node.js, MongoDB, Gemini API, AWS Amplify)} \\
        \vspace{-2pt}
        \resumeItemListStart
            \resumeItem{Built AI-powered study platform with PDF summarization, auto-generated quizzes, and real-time battle mode for competitive learning.}
            \resumeItem{Integrated Gemini API for intelligent content generation and WebSockets for real-time multiplayer study battles.}
            \resumeItem{\href{https://github.com/Isurusajan/Ai-Study-Buddy}{\textcolor{primaryblue}{github.com/Isurusajan/Ai-Study-Buddy}}}
        \resumeItemListEnd
        
    \resumeProjectHeading
        {\textbf{AI Image Generator}}{}
        \vspace{-3pt}
        \textit{\small (React.js, Node.js, MongoDB, Replicate API)} \\
        \vspace{-2pt}
        \resumeItemListStart
            \resumeItem{Built AI image generator with text-to-image conversion and community showcase wall for sharing artwork.}
            \resumeItem{Integrated Replicate API with user authentication and responsive design.}
            \resumeItem{\href{https://github.com/isurusajan/ai-image-generator}{\textcolor{primaryblue}{github.com/isurusajan/ai-image-generator}}}
        \resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-4pt}

\end{paracol}

\end{document}
